%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {DECIPHER, SNU Blockchain Academy} % Organization
    {Seoul, Republic of Korea} % Location
    {Mar. 2026 - Present} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Air Defense Artillery Operator} % Job title
    {Republic of Korea Air Force} % Organization
    {Republic of Korea} % Location
    {May 2024 - Feb. 2026} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained systems and conducted simulation-based training.}
        \item {Participated in annual live-fire air defense exercises, engaging aerial targets.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {DALPHA} % Organization
    {Seoul, Republic of Korea} % Location
    {Dec. 2023 - May 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a full-time software engineering intern in the AI team, automating diverse business pipelines for enterprise clients.}
        \item {Developed an automated layout and resizing engine using Layout-aware VAEs and Flexbox grids to export editable PSD files for further manual refinement.}
        \item {Migrated image generation workflows to ComfyUI via modular node-based graphs for VTON and background generation, enabling reproducible and high-speed B2B production.}
        \item {Built e-commerce tools using vector embeddings for large-scale catalog clustering and deployed RAG-based customer service chatbots to provide grounded, hallucination-free responses.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
